### 2015-11-30 fundamentals/impl.tex
proof of principle -> proof-of-principle

Cyclopts \cite{gidden_cyclopts_2015}, a proof of principle design and
implementation of a \Cyclus-enabled application on such a large compute system,
uses UW-Madison's HTCondor \gls{HTC} infrastructure to study DRE performance and
outcomes. For example, an investigation of the effect of solution degeneracy, a
commonly observed phenomenon in scenarios with individual facilities and basic
(e.g., commodity-only) preference definitions, was performed for three different
fuel cycles: once-through, \gls{MOX} fast reactor-thermal reactor cycles, and
\gls{MOX}-\gls{ThOX} recycle in fast reactors-thermal reactor cycles. Objective
coefficients were generated based on two factors: commodity-facility pairings
and facility location. The population of the possible values of
commodity-facility pairings is always small ($\mathcal{O}(10)$). The size of the
population of possible values of the location effect was investigated for values
of zero, ten, and infinity (i.e., any real number). The study additionally
included an investigation of problem-scaling behavior in order to quantify the
magnitude and rate-of-increase of DRE solution times as a function of the
simulation-entity population for each fuel
cycle\cite{gidden_agent-based_2015}. In total, Cyclopts has run over $10^5$
jobs, comprising more than 60,000 compute hours. The \gls{HTC} infrastructure
has separately been utilized to run and collect information from full \Cyclus
simulations running in parallel on $10^3$ machines reliably for order $10^5$
simulations.

>>>>

Cyclopts \cite{gidden_cyclopts_2015}, a proof-of-principle design and
implementation of a \Cyclus-enabled application on such a large compute system,
uses UW-Madison's HTCondor \gls{HTC} infrastructure to study DRE performance and
outcomes. For example, an investigation of the effect of solution degeneracy, a
commonly observed phenomenon in scenarios with individual facilities and basic
(e.g., commodity-only) preference definitions, was performed for three different
fuel cycles: once-through, \gls{MOX} fast reactor-thermal reactor cycles, and
\gls{MOX}-\gls{ThOX} recycle in fast reactors-thermal reactor cycles. Objective
coefficients were generated based on two factors: commodity-facility pairings
and facility location. The population of the possible values of
commodity-facility pairings is always small ($\mathcal{O}(10)$). The size of the
population of possible values of the location effect was investigated for values
of zero, ten, and infinity (i.e., any real number). The study additionally
included an investigation of problem-scaling behavior in order to quantify the
magnitude and rate-of-increase of DRE solution times as a function of the
simulation-entity population for each fuel
cycle\cite{gidden_agent-based_2015}. In total, Cyclopts has run over $10^5$
jobs, comprising more than 60,000 compute hours. The \gls{HTC} infrastructure
has separately been utilized to run and collect information from full \Cyclus
simulations running in parallel on $10^3$ machines reliably for order $10^5$
simulations.
